---
title: "TPMS"
author: "SS"
date: "3/16/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=T)
source("tpms.R")
```

## Odyssey

From http://opengarages.org/handbook/ebook/, TPMS data can be exploted in the following ways: 

• Send an impossible condition to the engine control unit (ECU), causing a fault that could then be exploited

• Trick the ECU into overcorrecting for spoofed road conditions

• Put the TPMS receiver or the ECU into an unrecoverable state that might cause a driver to pull over to check for a reported flat or that might even shut down the vehicle

• Track a vehicle based on the TPMS unique IDs

• Spoof the TPMS signal to set off internal alarms 

This project uses the code at https://github.com/jboone/gr-tpms to capture TPMS data. The author's talk, using an earlier version of the code, can be found here: http://www.youtube.com/watch?v=bKqiq2Y43Wg. Previous research on the topic can be found at https://web.wpi.edu/Pubs/E-project/Available/E-project-091115-154458/unrestricted/MQP_piscitelli_arnold_2015.pdf, and security vulnerabilities discussed in more depth at http://www.winlab.rutgers.edu/~gruteser/papers/xu_tpms10.pdf/.

Distribution of tire IDs

```{r odyssey}
odyssey <- analyzeOdyssey() %>% rename(sensorID=`tireID = substr(packet, 25, 56)`)
table(odyssey$sensorID)
```

First 3 bytes, statistical distribution

```{r}
bytes <- lapply(seq.int(1,3), function(x) {
        byte <- analyzePacket(odyssey$packet,x*8-7,x*8)
        cat(c("Byte ", x, ":"), sep="", fill=T)
        print(table(byte),dnn=NULL)
        #cat("By trip")
        #print(table(odyssey$trip,byte,odyssey$tireID,dnn=NULL))
        byte
})
```

```{r}
plotCountBy(odyssey, sensorID, bytes[[1]]) + ggtitle("Byte 1 Distribution By Sensor ID")
```

```{r}
plotCountBy(odyssey,sensorID) + ggtitle("Sensor Distribution By Trip") 
```

```{r}
odyssey.all <- analyzeOdyssey(T)
plotCountBy(odyssey.all,preamble) + ggtitle("Preamble Distribution By Trip")
```

```{r}
plotCountBy(odyssey,sensorID,bitrate) + ggtitle("Sensor ID Distribution By Bitrate")
```

```{r}
# Get 4 most commonly occuring sensor IDs
odyssey.mine <- odyssey %>% count(sensorID) %>% top_n(4, n)
odyssey.mine <- filter(odyssey, sensorID %in% 
                               odyssey.mine$sensorID)
plotCountBy(odyssey.mine, sensorID) + ggtitle("Sensor Distribution By Trip, Filtered")
bytes.mine <- lapply(seq.int(1,3), function(x) {analyzePacket(odyssey.mine$packet,x*8-7,x*8)})

odyssey.mine<-ungroup(odyssey.mine) %>% mutate(byte1=unbinary(bytes.mine[[1]]),
                                               byte2=unbinary(bytes.mine[[2]]),
                                               byte3=unbinary(bytes.mine[[3]])) %>% 
        group_by(trip, sensorID)

plotCountBy(odyssey.mine, sensorID, byte1) + ggtitle("Byte 1 by Sensor ID")
plotCountBy(odyssey.mine, sensorID, byte2) + ggtitle("Byte 2 by Sensor ID")
plotCountBy(odyssey.mine, sensorID, byte3) + ggtitle("Byte 3 by Sensor ID")

odyssey.mine <- mutate(odyssey.mine, date=ymd_hms(date))
ggplot(odyssey.mine, aes(date, byte2)) + geom_point(aes(color=sensorID,alpha=.5)) + 
        facet_grid(.~trip, scales="free_x") + ggtitle("Byte2 by trip") +
        theme(legend.position="bottom", axis.text.x=element_text(angle=90, hjust=1))

ggplot(odyssey.mine, aes(date, byte3)) + geom_point(aes(color=sensorID,alpha=.5)) + 
        facet_grid(.~trip, scales="free_x") + ggtitle("Byte3 by trip") + 
        theme(legend.position="bottom", axis.text.x=element_text(angle=90, hjust=1))
```