---
title: "TPMS"
author: "SS"
date: "3/16/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=T)
source("tpms.R")
```

## Odyssey

From http://opengarages.org/handbook/ebook/, TPMS data can be exploted in the following ways: 

• Send an impossible condition to the engine control unit (ECU), causing a fault that could then be exploited
• Trick the ECU into overcorrecting for spoofed road conditions
• Put the TPMS receiver or the ECU into an unrecoverable state that might cause a driver to pull over to check for a reported flat or that might even shut down the vehicle
• Track a vehicle based on the TPMS unique IDs
• Spoof the TPMS signal to set off internal alarms 

This project uses the code at https://github.com/jboone/gr-tpms to capture TPMS data. The author's talk, using an earlier version of the code, can be found here: http://www.youtube.com/watch?v=bKqiq2Y43Wg. Previous research on the topic can be found at https://web.wpi.edu/Pubs/E-project/Available/E-project-091115-154458/unrestricted/MQP_piscitelli_arnold_2015.pdf, and security vulnerabilities discussed in more depth at http://www.winlab.rutgers.edu/~gruteser/papers/xu_tpms10.pdf/.

Distribution of tire IDs

```{r odyssey}
odyssey <- analyzeOdyssey()
table(odyssey$`tireID = substr(packet, 25, 56)`)
```

First 3 bytes, statistical distribution

```{r}
bytes <- lapply(seq.int(1,3), function(x) {
        byte <- analyzePacket(odyssey$packet,x*8-7,x*8)
        cat(c("Byte ", x, ":"), sep="", fill=T)
        print(table(byte),dnn=NULL)
        #cat("By trip")
        #print(table(odyssey$trip,byte,odyssey$tireID,dnn=NULL))
        byte
})
```

```{r}
plotCountBy(odyssey, `tireID = substr(packet, 25, 56)`, bytes[[1]]) + ggtitle("Byte 1 Distribution By Tire ID")
```

```{r}
plotCountBy(odyssey,`tireID = substr(packet, 25, 56)`) + ggtitle("Tire Distribution By Trip")
```

```{r}
odyssey.all <- analyzeOdyssey(T)
plotCountBy(odyssey.all,preamble) + ggtitle("Preamble Distribution By Trip")
```

```{r}
plotCountBy(odyssey,`tireID = substr(packet, 25, 56)`,bitrate) + ggtitle("Tire ID Distribution By Bitrate")
```